Regular singular Volterra equations on complex domains

### 2024-08-05 sima/reg-sing-volterra_sima.tex
Settle on explicit moving point notation
Drop the old-notation versions of the equations.

Let $\holo(\domain)$ be the space of holomorphic functions on $\domain$.
\begin{definition}\label{defn:volterra}
A {\em holomorphic Volterra operator} on $\domain$ is a linear operator
\[\genvolterra\colon\holo(\domain)\to\holo(\domain) \]
defined by an integral
\begin{oldnot}
\[ [\genvolterra\,\varphi](a) = \int_{\zeta = 0}^a \genker(a, \cdot)\,\varphi\;d\zeta \]
\end{oldnot}
\begin{newnot}\begin{todo}[Possibility: use moving point to write kernel with both arguments]\end{todo}
\[ [\genvolterra\,\varphi](a) = \int_{\zeta(a') = 0}^a \genker(a, a')\,\varphi(a')\;d\zeta(a') \]
\end{newnot}
\begin{newnot}\begin{todo}[Possibility: ``integration along $\zeta''$ with $\zeta'$ fixed]\end{todo}
\[ \genvolterra\,\varphi = \int_{0}^{\zeta} \genker\,\varphi''\;d\zeta''\Big|_{\zeta' = \zeta} \]
\end{newnot}
in which the {\em kernel} $w$ is a holomorphic function on $\Omega^2$.
\end{definition}
\begin{definition}
A holomorphic Volterra operator is {\em separable} if its kernel factors as a product of two functions, one on each factor of $\Omega^2$.
\end{definition}
For the prototype operator $\hardpart$, we will suppose that the kernel $\hardker$ can be written as a ratio
\[ \hardker(a, a') = - \frac{q(a')}{p(a)}, \]
for some $p, q \in \mathcal{H}(\Omega)$. \end{rev}\begin{revtwo}Explicitly,
\[ \big[\hardpart \varphi\big](a) = - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\varphi\;d\zeta\,. \]
\end{revtwo}

@@

We now perturb $\hardpart$ to a more general operator $\volterra = \hardpart +\softpart$. \begin{revtwo}The perturbation
\begin{oldnot}
\[ [\softpart\,\varphi](a) := \int_{\zeta = 0}^a \softker(a, \cdot)\,\varphi\;d\zeta \]
\end{oldnot}
\begin{newnot}
\[ [\softpart\,\varphi](a) := \int_{\zeta(a') = 0}^a \softker(a, a')\,\varphi(a')\;d\zeta(a') \]
\end{newnot}
will be non-separable,\end{revtwo}\footnote{Unless $\softpart$ is zero, of course.} but it will have a regularizing effect, as we will show in Proposition \ref{prop:smoothing}. To get the smoothing effect, we will require \revtwotext{the kernel $\softker$} to vanish to some order $\gamma > 0$ on the diagonal in $\domain^2$. This requirement, combined with two others, will be made precise in Condition~\eqref{cond:eps-lambda}.

@@

\subsection{Main results}\label{sec:results}
We want to show that when $\volterra$ is a regular singular Volterra operator of the kind described in Section~\ref{setting:perturbed}, the equation $f = \volterra f$ has a unique solution of a certain form. For the prototypical operator $\hardpart$ described in Section~\ref{setting:basic}, this solution can be written explicitly.
\begin{theorem}\label{thm:basic_volterra}
\begin{revtwo}Suppose the operator%%$\hardpart$
\[ \big[\hardpart \varphi\big](a) := - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\varphi\;d\zeta \]
\end{revtwo}
satisfies {\em Condition \eqref{cond:sing}}. Then the equation
\begin{equation}\label{eq:hardpart}
f = \hardpart f    
\end{equation}
has the {\em prototype solution}
\begin{equation}\label{eqn:test_solution}
\solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
\end{equation}
Changing the base point $b \in \domain$ \revtext{only} multiplies $f_0$ by a non-zero constant.
\end{theorem}
We will prove this result in Section~\ref{sec:construction}.

The solution $\solproto$ from Theorem~\ref{thm:basic_volterra} has, at worst, a mild power-law singularity at $\zeta = 0$. \revtext{When $\hardpart$ is especially regular, $\solproto$ also grows at most exponentially as $|\zeta| \to \infty$.} The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties. \begin{revtwo}We will state our results in terms of the spaces $\singexpalg{\sigma}(\domain)$, which are defined as unions of normed spaces. Every function $f \in \singexpalg{\sigma}(\domain)$ has a finite norm
\[ \|f\|_{\sigma,\Lambda} := \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f| \]
for some $\Lambda \in \R$.
\end{revtwo}
\begin{theorem}\label{thm:proto-growth}
\begin{revtwo}Suppose the operator%%$\hardpart$
\[ \big[\hardpart \varphi\big](a) := - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\varphi\;d\zeta \]
\end{revtwo}
satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.

@@

\revtext{The perturbed equation $f = \volterra f$ is more complicated, but its regular singularity at $\zeta = 0$ is essentially the same.} We might therefore \revtext{expect a solution} that looks like $\solproto$ near the singularity, differing only by a less singular perturbation. If we strengthen the constraints on $\hardpart$ a little more, this expectation is fulfilled.
\begin{theorem}\label{thm:general_volterra}
Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and \begin{revtwo}the perturbation
\begin{oldnot}
\[ [\softpart\,\varphi](a) := \int_{\zeta = 0}^a \softker(a, \cdot)\,\varphi\;d\zeta \]
\end{oldnot}
\begin{newnot}
\[ [\softpart\,\varphi](a) := \int_{\zeta(a') = 0}^a \softker(a, a')\,\varphi(a')\;d\zeta(a') \]
\end{newnot}
\end{revtwo}
satisfies {\em Condition~\eqref{cond:eps-lambda}}. Then the equation
\[ f = \volterra f \]
has a unique solution $f$ in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\gamma}(\Omega) \]
of the space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the space $\singexpalg{\tau-1}(\domain)$.
\end{theorem}
\begin{rev}\begin{corollary}\label{cor:expand_uniq}
Under the conditions of Theorem~\ref{thm:general_volterra}, for any $\rho > \tau$, the equation $f = \volterra f$ has at most one solution in $f_0 + \singexpalg{\rho-1}(\Omega)$. 
\end{corollary}\end{rev}
This result will follow from a more general result about inhomogeneous equations.
\begin{lemma}\label{lem:perturbed_volterra}
Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}. Suppose we are also given a function $g$, which for some $\rho > \tau$ belongs to the space $\singexpalg{\rho-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Then the inhomogeneous equation
\[ f = \volterra f + g, \]
has a unique solution $f$ in the space $\singexpalg{\rho-1}(\Omega)$.
\end{lemma}
We will prove Lemma~\ref{lem:perturbed_volterra} in Sections \ref{sec:V is a contraction}--\ref{sec:existence and uniqueness}, using the contraction mapping theorem. The heart of the argument is Proposition~\ref{prop:get-contraction}, which shows us how to find relevant subspaces where $\volterra$ is a contraction.

@@

\begin{oldnot}

@@

|\zeta(a)|^{-(\sigma+\gamma)} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert
&\leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |f| \, |d\zeta| \\
&\leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \|f\|_{\sigma,\Lambda} \, |d\zeta| 

@@

\end{oldnot}
\begin{newnot}

@@

|\zeta(a)|^{-(\sigma+\gamma)} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert
&\leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta(a')=0}^a |\softker(a,a')|\, |f(a')| \, |d\zeta(a')| \\
&\leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta(a')=0}^a |\softker(a,a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \|f\|_{\sigma,\Lambda} \, |d\zeta(a')|

@@

\end{newnot}
By Condition~\eqref{cond:eps-lambda}, \begin{todo}[notation updated]\end{todo}
\begin{newnot}
\int_{\zeta=0}^a |\softker(a,a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \, |d\zeta(a')| &\lesssim \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\gamma}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
&\lesssim |\zeta(a)|^{\gamma+\sigma} \int_{0}^1 (1-t)^\gamma e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
&\lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,  \int_{0}^1 (1-t)^\gamma  t^{\sigma}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)| t}\;dt\\
&\lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)|}\int_{0}^1 (1-t)^\gamma  t^{\sigma}\;dt.
\end{newnot}

@@

\begin{oldnot}
\[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}. \]
\end{oldnot}
\begin{newnot}
\[ \int_{\zeta(a')=0}^a |\softker(a, a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \, |d\zeta(a')| \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}. \]
\end{newnot}

@@

\begin{oldnot}
\[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}, \]
\end{oldnot}
\begin{newnot}
\[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta(a')=0}^a |\softker(a,a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \, |d\zeta(a')| \lesssim \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}, \]    
\end{newnot}

@@

\begin{oldnot}
\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta = 0}^a |k(a,\cdot)\,\varphi\;d\zeta| \]
\end{oldnot}
\begin{newnot}
\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta(a') = 0}^a |k(a, a')\,\varphi(a')\;d\zeta(a')| \]
\end{newnot}

@@

|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta = 0}^a |k(a,\cdot)|\,|\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}\;|d\zeta| \\
& = \|\varphi\|_{\rho-1, \Lambda}  \int_{\zeta = 0}^a |k(a, \cdot)|\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|

@@

\end{oldnot}
\begin{newnot}
|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta(a') = 0}^a |k(a, a')|\,|\zeta(a')|^{\rho-1}\,e^{\Lambda |\zeta(a')|}\,\|\varphi\|_{\rho-1, \Lambda}\;|d\zeta(a')| \\
& = \|\varphi\|_{\rho-1, \Lambda}  \int_{\zeta(a') = 0}^a |k(a, a')|\,\left|\frac{\zeta(a')}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta(a')|)}\;|d\zeta(a')|
\end{newnot}

@@

|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le

@@

|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le \sigma \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\

@@

\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_{\zeta = 0}^a M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|. \]

@@

|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le \|\varphi\|_{\rho-1, \Lambda} \int_0^1 M e^{\lambda |\zeta(a)|(1 - t)}\,t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\

@@

\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt. \]

>>>>

Let $\holo(\domain)$ be the space of holomorphic functions on $\domain$.
\begin{definition}\label{defn:volterra}
A {\em holomorphic Volterra operator} on $\domain$ is a linear operator
\[\genvolterra\colon\holo(\domain)\to\holo(\domain) \]
defined by an integral
\begin{revtwo}
\[ [\genvolterra\,\varphi](a) = \int_{\zeta(a') = 0}^a \genker(a, a')\,\varphi(a')\;d\zeta(a') \]
\end{revtwo}
in which the {\em kernel} $w$ is a holomorphic function on $\Omega^2$.
\end{definition}
\begin{definition}
A holomorphic Volterra operator is {\em separable} if its kernel factors as a product of two functions, one on each factor of $\Omega^2$.
\end{definition}
For the prototype operator $\hardpart$, we will suppose that the kernel $\hardker$ can be written as a ratio
\[ \hardker(a, a') = - \frac{q(a')}{p(a)}, \]
for some $p, q \in \mathcal{H}(\Omega)$. \end{rev}\begin{revtwo}Explicitly,
\[ \big[\hardpart \varphi\big](a) = - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\varphi\;d\zeta\,. \]
\end{revtwo}

@@

We now perturb $\hardpart$ to a more general operator $\volterra = \hardpart +\softpart$. \begin{revtwo}The perturbation
\[ [\softpart\,\varphi](a) := \int_{\zeta(a') = 0}^a \softker(a, a')\,\varphi(a')\;d\zeta(a') \]
will be non-separable,\end{revtwo}\footnote{Unless $\softpart$ is zero, of course.} but it will have a regularizing effect, as we will show in Proposition \ref{prop:smoothing}. To get the smoothing effect, we will require \revtwotext{the kernel $\softker$} to vanish to some order $\gamma > 0$ on the diagonal in $\domain^2$. This requirement, combined with two others, will be made precise in Condition~\eqref{cond:eps-lambda}.

@@

\subsection{Main results}\label{sec:results}
We want to show that when $\volterra$ is a regular singular Volterra operator of the kind described in Section~\ref{setting:perturbed}, the equation $f = \volterra f$ has a unique solution of a certain form. For the prototypical operator $\hardpart$ described in Section~\ref{setting:basic}, this solution can be written explicitly.
\begin{theorem}\label{thm:basic_volterra}
\begin{revtwo}Suppose the operator%%$\hardpart$
\[ \big[\hardpart \varphi\big](a) := - \int_{\zeta(a')=0}^{a} \frac{q(a')}{p(a)}\,\varphi(a')\;d\zeta(a') \]
\end{revtwo}
satisfies {\em Condition \eqref{cond:sing}}. Then the equation
\begin{equation}\label{eq:hardpart}
f = \hardpart f    
\end{equation}
has the {\em prototype solution}
\begin{equation}\label{eqn:test_solution}
\solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
\end{equation}
Changing the base point $b \in \domain$ \revtext{only} multiplies $f_0$ by a non-zero constant.
\end{theorem}
We will prove this result in Section~\ref{sec:construction}.

The solution $\solproto$ from Theorem~\ref{thm:basic_volterra} has, at worst, a mild power-law singularity at $\zeta = 0$. \revtext{When $\hardpart$ is especially regular, $\solproto$ also grows at most exponentially as $|\zeta| \to \infty$.} The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties. \begin{revtwo}We will state our results in terms of the spaces $\singexpalg{\sigma}(\domain)$, which are defined as unions of normed spaces. Every function $f \in \singexpalg{\sigma}(\domain)$ has a finite norm
\[ \|f\|_{\sigma,\Lambda} := \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f| \]
for some $\Lambda \in \R$.
\end{revtwo}
\begin{theorem}\label{thm:proto-growth}
\begin{revtwo}Suppose the operator
\[ \big[\hardpart \varphi\big](a) := - \int_{\zeta(a')=0}^{a} \frac{q(a')}{p(a)}\,\varphi(a')\;d\zeta(a') \]
\end{revtwo}
satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.

@@

\revtext{The perturbed equation $f = \volterra f$ is more complicated, but its regular singularity at $\zeta = 0$ is essentially the same.} We might therefore \revtext{expect a solution} that looks like $\solproto$ near the singularity, differing only by a less singular perturbation. If we strengthen the constraints on $\hardpart$ a little more, this expectation is fulfilled.
\begin{theorem}\label{thm:general_volterra}
Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and \begin{revtwo}the perturbation
\[ [\softpart\,\varphi](a) := \int_{\zeta(a') = 0}^a \softker(a, a')\,\varphi(a')\;d\zeta(a') \]
\end{revtwo}
satisfies {\em Condition~\eqref{cond:eps-lambda}}. Then the equation
\[ f = \volterra f \]
has a unique solution $f$ in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\gamma}(\Omega) \]
of the space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the space $\singexpalg{\tau-1}(\domain)$.
\end{theorem}
\begin{rev}\begin{corollary}\label{cor:expand_uniq}
Under the conditions of Theorem~\ref{thm:general_volterra}, for any $\rho > \tau$, the equation $f = \volterra f$ has at most one solution in $f_0 + \singexpalg{\rho-1}(\Omega)$. 
\end{corollary}\end{rev}
This result will follow from a more general result about inhomogeneous equations.
\begin{lemma}\label{lem:perturbed_volterra}
Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}. Suppose we are also given a function $g$, which for some $\rho > \tau$ belongs to the space $\singexpalg{\rho-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Then the inhomogeneous equation
\[ f = \volterra f + g, \]
has a unique solution $f$ in the space $\singexpalg{\rho-1}(\Omega)$.
\end{lemma}
We will prove Lemma~\ref{lem:perturbed_volterra} in Sections \ref{sec:V is a contraction}--\ref{sec:existence and uniqueness}, using the contraction mapping theorem. The heart of the argument is Proposition~\ref{prop:get-contraction}, which shows us how to find relevant subspaces where $\volterra$ is a contraction.

@@

\begin{revtwo}

@@

& |\zeta(a)|^{-(\sigma+\gamma)} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert \\
& \qquad \leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta(a')=0}^a |\softker(a,a')|\, |f(a')| \, |d\zeta(a')| \\
& \qquad \leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta(a')=0}^a |\softker(a,a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \|f\|_{\sigma,\Lambda} \, |d\zeta(a')|\,.

@@

\end{revtwo}
By Condition~\eqref{cond:eps-lambda},
\begin{revtwo}

@@

& \int_{\zeta(a')=0}^a |\softker(a,a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \, |d\zeta(a')| \\
& \qquad \lesssim \int_{\zeta(a')=0}^a \frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} |\zeta(a')|^{\sigma}\, e^{\Lambda|\zeta(a')|}\;|d\zeta(a')|\\
& \qquad \lesssim |\zeta(a)|^{\gamma+\sigma} \int_{0}^1 (1-t)^\gamma e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
& \qquad \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,  \int_{0}^1 (1-t)^\gamma  t^{\sigma}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)| t}\;dt\\
& \qquad \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)|}\int_{0}^1 (1-t)^\gamma  t^{\sigma}\;dt.

@@

\end{revtwo}

@@

\begin{revtwo}
\[ \int_{\zeta(a')=0}^a |\softker(a, a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \, |d\zeta(a')| \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}\,. \]
\end{revtwo}

@@

\begin{revtwo}
\[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta(a')=0}^a |\softker(a,a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \, |d\zeta(a')| \lesssim \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}\,, \]    
\end{revtwo}

@@

\begin{revtwo}
\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta(a') = 0}^a |k(a, a')\,\varphi(a')\;d\zeta(a')| \]
\end{revtwo}

@@

&|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| \\
& \qquad \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta(a') = 0}^a |k(a, a')|\,|\zeta(a')|^{\rho-1}\,e^{\Lambda |\zeta(a')|}\,\|\varphi\|_{\rho-1, \Lambda}\;|d\zeta(a')| \\
& \qquad = \|\varphi\|_{\rho-1, \Lambda}  \int_{\zeta(a') = 0}^a |k(a, a')|\,\left|\frac{\zeta(a')}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta(a')|)}\;|d\zeta(a')|

@@

\end{revtwo}

@@

|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| & \le

@@

|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| & \le \sigma \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\

@@

\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| \le \|\varphi\|_{\rho-1, \Lambda} \int_{\zeta = 0}^a M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|. \]

@@

|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| & \le \|\varphi\|_{\rho-1, \Lambda} \int_0^1 M e^{\lambda |\zeta(a)|(1 - t)}\,t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\

@@

\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt. \]
